Anonymous provision of services via blockchain

### 2022-03-04 access.tex
results to result

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of local services via blockchain}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of local services via blockchain}

@@

A local service provider can employ our protocol to provide
services without collecting any personal information. Possible
applications for this protocol include anonymous clinical drug testing,
steroid testing, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service
provider.

@@

\begin{keywords}
Blockchain, anonymity, fair-exchange, physical delivery
\end{keywords}

@@

There is some services that would benefit from anonymous services, some examples are:
\begin{itemize}
    \item Patients willing to take a 
    test for drug, venereal diseases, paternity etc. have a strong incentive to keep the whole procedure private. Merely the fact that they took the test — without exposing the results — is suggestive enough to act as a premise in case of a conflict.

@@

In case of dispute, either due to exceeding deadlines or providing
incorrect results, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service 
provider.
%JS a np automatyczny zwrot środków?
%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

In our case, the customer is exchanging with the SP cryptocurrency and materials for the results.

@@

\item TTP-less: 
our protocol does not rely on a trusted-third party to conduct transactions in fairly manner. Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

The idea behind certified e-mails—and any other fair-exchange protocol—is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

@@

In this case, the role of Blockchain is to attest the public existence of decryption key at a particular point of time.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in section ~\ref{sec:future-work}.

@@

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time; deadline to pay for the transaction, and the deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.

    \item Proof-of-provision ($\mathrm{PoP}$) is proof that the SP published the results at a certain time. It defends the SP in case the customer unjustly starts a dispute after the results have been published. It consists of a content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
\end{enumerate}

@@

We need this functionality for two reasons: (1) Communicate the existence
of the results to the customer to whom the SP have no other
communication medium as the customer stays anonymous; (2) let the SP to proof the publication of results within the agreed with customer deadline.

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
at which the results has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the results at that time.

Without such a proof there would be no other means to settle the conflict between the customer claiming the results have not been published and the SP claiming the results have been published within the deadline.

@@

The relations between these terms are illustrated in the figure~\ref{fig:anonymity-diagram1}.

@@

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, he has to provide the results to the customer. The most natural approach would to be send the results via email of the dedicated platform. However, since the customer wants to stay anonymous, he doesn't want to expose his email address nor IP address. Moreover, in case of dispute, the SP should be able to prove that the results have been provided before the deadline.

One approach would be to post the results into a blockchain. Yet, storing data on a blockchain is very expensive. The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content addressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.

We take the same approach. Once the SP creates the results, he encrypts them using the previously provided encryption key; then publishes them into an IPFS network.

@@

%%%%%%%%%%% dotad sprawdzone
\section{The Protocol}\label{sec:protocol}

@@

\item The SP:
    \begin{itemize}
        \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
        \item Accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
    \end{itemize}

\item Justice:
    \begin{itemize}
        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{proof-of-justice}.
    \end{itemize}

\item Anonymous payments:
    \begin{itemize}
        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{sec:pseudo-anon}.
        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
    \end{itemize}

@@

\subsection{Messages}\label{messages}
In this section we describe the messages exchanged between the parties of the protocol.

\noindent \textbf
{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt results published on the storage network.

@@

\item $\mathrm{materials}$ - are the materials required to provide the service on. For example: sample of urine, blood, stool, saliva; legal documents, CDs, mails, photos, bank statement, or any other kind of evidence depending on the service.
\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the results.
\end{itemize}

@@

We assume the $\mathrm{PoD}$ to be an QR code printed on a paper receipt, but any other form that quarantee integrity, authenticity and non-repudiation can be used instead.

The ($\mathrm{PoD}$ can be then used as a evidence in case of a dispute.

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the PoD is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide the service results.
\item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

also:

\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)

\noindent \textbf
{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the results at a certain time. It defends the SP in case the customer unjustly starts a dispute after the results have been published. The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.

The $\mathrm{PoP}$ is an digital construction published by the SP on a message board.

@@

\noindent \textbf
{Payment attestation}\label{payment-attestation}

Payment attestation proves that the customer did the payment. Since the
evidences depends on the particular blockchain (see section ~\ref{payment-for-services}). We refer to them symbollicaly as
\(attestation\).

\noindent \textbf
{Results}\label{results}

We assume results to be documents in PDF format, but they can be
anything as long as they can be binary encoded and uploaded to IPFS. We
refer to them symbollicaly as \(results\).

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid}

Although content identifier (cid) is a term coined by IPFS
\cite{Contenta59}. However, since we our protocol does not depend on
this particular implementation of storage network, we let the cid be any
other identifier that securely and uniquely points to the content.

@@

In this section we describe each step of the protocol. The steps are
shown in the figure ~\ref{fig:protocol-diagram}.

@@

The customer collects all the $\mathrm{materials}$ required by the SP, generate an encryption $\mathrm{key}$ print it on a paper as a QR code, and pack them together into a package $\mathrm{pkg}$.

Symbolically: \[
\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
\]

@@

We assume this step to be fully physical, that is, $\mathrm{pkg}$ consist of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on paper receipt.

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via trusted person, the confirmation can be issued in person as well. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on message board (further extension to anonymous delivery system is discussed in section \ref{sec:future-work}).

Symbolically: 
\[
\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
\]
\[
(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
\]

@@

Having the PoD issued, the SP can not reject receiving the package. At this point the
customer should pay for the transaction with agreed upfront cryptocurrency system (see section~\ref{payment-for-services}).

@@

Symbolically: \[
\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
\]

\noindent \textbf
{Step 3. Provision of service}\label{step-3-provision-of-service} 
Once the transaction is paid the SP start the provision of service.

Symbolically: \[
\mathrm{results} \gets \mathrm{provision}(\mathrm{materials})
\]

\noindent \textbf
{Step 4. Results upload}\label{step-4-results-upload}

After the service is finished, some kind of output should be created. Next, the output is encrypted using encryption symmetric key $\mathrm{key}$ provided in the first step.

The encrypted results are then uploaded on content addressable network such as IPFS. As a result, the content identifier (cid) is returned.

Symbolically: 
\[
\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{results}))
\]

@@

When the results are published, the SP perform proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})\]
\[\mathrm{publish}(\mathrm{PoP})\]

@@

After delivering the package and paying for the transaction the customer subscribe to the message board and waits until the SP publish the proof of provision. The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.

Symbolically: \[
\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
\]

\noindent \textbf
{Step 7. Results download}\label{step-7-results-download} Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.

Symbolically: \[
\mathrm{results} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
\]

@@

We analyse the fairness of the protocol by representing it as a interactive non-cooperative game.

@@

\begin{itemize}
\item
  Neutral position (•): when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item
  Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, paid for a service in advance.
\item
  Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
\end{itemize}

There are many actions that each party can take, but we group them together into two categories:

@@

\item
  Normal: taking the action prescribed by the protocol.
\item
  Abnormal: everything that deviates from designed steps of the protocol. For example, sending arbitrary message, skipping some step, repeating step, timing out.
\end{enumerate}

Moreover, at any step of the protocol the customer can start a dispute; therefore, another dimension with two positions has to be considered:

@@

\item
  Agree: the customer agree with the action, and therefore does not start a dispute.
\item
  Start a dispute: the customer does not agree with the action and therefore start a dispute.
\end{enumerate}

@@

The protocol terminate after last step, after starting a dispute, or after a party hasn't completed it's designated action in time. Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.

Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer. To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

For the analysis purpose we state plausable assumptions listed below.

Assumptions:

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialise and complete the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other step is considered abnormal and gets ignored. For example paying for the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any action.
\item
  Losing the dispute leads to punishment that is greater than any reward, which leads to disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•).
\item
  Both the customer and the SP are rational (selfish). They always prefer go from worst position to better position, but also risk temporary worst position in favour for later better position iff it's assured that they won't stuck in worst position.
\end{itemize}

@@

The table in figure~\ref{fig:positions} shows the positions of each party after each possible action taken.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-table-of-positions.png}
\centering
\caption{Table of positions after each step of protocol}
\label{fig:positions}
\end{figure}

Below we give the description for each step and rationale of the outcome position.

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position. One would argue that the customer has put effort of
    delivering the materials to the SP, or that the sample is valuable.
    We assume that the sample without personal information is useless
    and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{1, c, \mathrm{d}} = -\), the customer lose the case as the SP has still opportunity to publish proof-of-provision within timeframe.
  \item
    \(\sigma_{1, s, \mathrm{d}} = \sbullet\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol and move to the non-disadvantaged
  position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
\item
  The SP can do nothing and end up in non-disadvantaged position
  \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
  \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
\end{itemize}

@@

SP has published \textbf{incorrect} results on time:

>>>>

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of services via blockchain}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Anonymous provision of services via blockchain}

@@

A service provider can employ our protocol to provide
services without collecting any personal information. Possible
applications for this protocol include anonymous clinical drug testing,
steroid, parenting testing, anonymous legal advice, or
anonymous financial trustworthiness evaluation.

In case of dispute, either due to exceeding deadlines or providing
incorrect result, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service
provider.

@@

\begin{keywords}
fair-exchange, blockchain, anonymity,  physical delivery, services
\end{keywords}

@@

There is some services that would benefit from anonymous services, some examples are:
\begin{itemize}
    \item Patients willing to take a 
    test for drug, venereal diseases, paternity etc. have a strong incentive to keep the whole procedure private. Merely the fact that they took the test without exposing the result is suggestive enough to act as a premise in case of a conflict.

@@

In case of dispute, either due to exceeding deadlines or providing
incorrect result, the customer can disclose the whole interaction and
prove to justice (police or court) the misbehavior of the service 
provider.
%JS a np automatyczny zwrot środków?
%SP to wymagałoby wprowadzenie depozytu co bardzo komplikuje cały system. Co więcej miałoby to sens tylko wtedy gdyby użyć "zdecentralizowanych sądów" (Future Work/Justice).

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

In our case, the customer is exchanging with the SP cryptocurrency and materials for the result of a service.

@@

\item TTP-less: 
our protocol does not rely on a trusted-third party to conduct transactions in fairly manner. Only in case of dispute   the centralized justice is involved (the justice decentralization is discussed in Section ~\ref{sec:future-work}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In Section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the background related to fair-exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, Section~\ref{sec:conclusion} concludes the paper.

@@

The idea behind certified e-mails and any other fair-exchange protocol is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publish on blockchain (or TTP in general) a proof of delivery and the decryption key.
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

@@

In this case, the role of blockchain is to attest the public existence of decryption key at a particular point of time.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

@@

Possible directions toward semi-autonomous decentralised resolution
system are discussed in Section ~\ref{sec:future-work}.

@@

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time; deadline to pay for the transaction; deadline to provide a result of the service; randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.

    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time. It defends the SP in case the customer unjustly starts a dispute after the result have been published. It consists of a content identifier as specified in Section ~\ref{storage-network}; the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the result is made by the content identifier (cid) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
\end{enumerate}

@@

We need this functionality for two reasons: (1) Communicate the existence
of the result to the customer to whom the SP have no other
communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
at which the result has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.

Without such a proof there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.

@@

The relations between these terms are illustrated in the Figure~\ref{fig:anonymity-diagram1}.

@@

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, he has to provide the result to the customer. The most natural approach would to be send the result via email of the dedicated platform. However, since the customer wants to stay anonymous, he doesn't want to expose his email address nor IP address. Moreover, in case of dispute, the SP should be able to prove that the result has been provided before the deadline.

One approach would be to post the result into a blockchain. Yet, storing data on a blockchain is very expensive. The most common workaround (\cite{shahid2020blockchain, wang2019auditable, chen2017improved, Usageide95}) is to publish the data to the IPFS \cite{benet2014ipfs}—a content addressable peer-to-peer storage network—and publish to a blockchain just a content identifier (cid) that uniquely points to the content stored on the IPFS.

We take the same approach. Once the SP creates the result, he encrypts it using the previously provided encryption key and uploads it to IPFS network.

@@

\section{The Protocol}\label{sec:protocol}

@@

\item The SP:
    \begin{itemize}
        \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
        \item Accepts payments with anonymous cryptocurrencies as described in Section~\ref{payment-for-services}.
    \end{itemize}

\item Justice:
    \begin{itemize}
        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in Section~\ref{proof-of-justice}.
    \end{itemize}

\item Anonymous payments:
    \begin{itemize}
        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in Section~\ref{sec:pseudo-anon}.
        \item Supports uniquely identifying transaction either via separate address, memo field, or other similar mechanisms as described in Section ~\ref{payment-for-services}. 
    \end{itemize}

@@

\subsection{Messages}\label{messages}
In this section, we describe the messages exchanged between the parties of the protocol.

\noindent \textbf
{Package}\label{package} is a physical container prepared by the customer encompassing all $\mathrm{materials}$ required by the SP to provide the service, and an encryption $\mathrm{key}$ used to encrypt the result published on the storage network.

@@

\item $\mathrm{materials}$ - are the materials required to provide the service. For example samples of urine, blood, stool, saliva; legal documents, CDs, emails, photos, bank statements, or any other kind of evidence depending on the service.
\item $\mathrm{key}$ - symmetric key used to encrypt and decrypt the result.
\end{itemize}

@@

We assume the $\mathrm{PoD}$ to be a QR code printed on a paper receipt, but any other form that guarantees integrity, authenticity, and non-repudiation can be used instead.

The ($\mathrm{PoD}$ can be then used as evidence in case of a dispute.

@@

\item $\mathrm{T}_\mathrm{issue}$ - time at which the PoD is issued.
\item
  $\mathrm{T}_\mathrm{pay}$ - deadline to pay for the transaction.
\item
  $\mathrm{T}_\mathrm{provide}$ - deadline to provide a result of the service.
\item $\mathrm{nonce}$ - randomly generated number uniquely identifying the transaction.
\item $\mathrm{sig}_\mathrm{SP}$ - the SP's signature guaranteeing non-repudiation.
\end{itemize}

also:
\(\mathrm{T}_\mathrm{issue} < \mathrm{T}_\mathrm{pay} < \mathrm{T}_\mathrm{provide}\)

\noindent \textbf
{Proof of provision ($\mathrm{PoP}$)}\label{proof-of-provision} is proof that the SP published the result at a certain time. It defends the SP in case the customer unjustly starts a dispute after the result has been published. The connection between $\mathrm{PoP}$ and the result is made by the content identifier ($(\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.

The $\mathrm{PoP}$ is a digital construction published by the SP on the message board.

@@

\noindent \textbf
{Payment attestation}\label{payment-attestation}
proves that the customer did the payment. Since the
evidence depends on the particular blockchain (see Section ~\ref{payment-for-services}). We refer to them symbolically as
\(attestation\).

\noindent \textbf
{Result}\label{results} is assumed to be document in PDF format, but any other format is allowed as long as it can be binary encoded and uploaded to IPFS. We refer to it symbolically as $result$.

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid}  is a term coined by IPFS
\cite{Contenta59}  
. However, since our protocol does not depend on
this particular implementation of the storage network, we let the cid be any
other identifier that securely and uniquely points to the content.

@@

In this section, we describe each step of the protocol. The steps are
shown in the Figure ~\ref{fig:protocol-diagram}.

@@

The customer collects all the $\mathrm{materials}$ required by the SP, generates an encryption $\mathrm{key}$ prints it on a paper as a QR code, and packs them together into a package $\mathrm{pkg}$.

Symbolically: 
$
\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
$

@@

We assume this step to be fully physical, that is, $\mathrm{pkg}$ consists of physical materials, $\mathrm{PoD}$ is in a form of e.g., QR code printed on a paper receipt.

$\mathrm{PoD}$ could be published on a message board (similarly to $\mathrm{PoP}$); however, since the $\mathrm{pkg}$ is delivered personally or via a trusted person, the confirmation can be issued in person as well. If we would like to hire a courier to deliver our $\mathrm{pkg}$, then the $\mathrm{PoD}$ would have to be published on the message board (further extension to the anonymous delivery system is discussed in Section \ref{sec:future-work}).

Symbolically: 
$
\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
$

$
(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
$

@@

Having the PoD issued, the SP can not reject receiving the package. At this point the
customer should pay for the transaction with an agreed upfront cryptocurrency system (see Section~\ref{payment-for-services}).

@@

Symbolically: 
$
\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
$

\noindent \textbf
{Step 3. Provision of service}\label{step-3-provision-of-service} 
Once the transaction is paid the SP starts the provision of service.

Symbolically: 
$
\mathrm{result} \gets \mathrm{provision}(\mathrm{materials})
$

\noindent \textbf
{Step 4. Upload result }\label{step-4-results-upload}

After the service is finished, some result should be created. Next, the result is encrypted using encryption symmetric $\mathrm{key}$ provided in the first step.

The encrypted result is then uploaded on the content addressable network such as IPFS. In return the content identifier (cid) is created.

Symbolically: 
$
\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{result}))
$

@@

When the result is published, the SP performs proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
$
\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})
$

$
\mathrm{publish}(\mathrm{PoP})
$

@@

After delivering the package and paying for the transaction the customer subscribes to the message board and waits until the SP publishes the proof of provision. The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.

Symbolically: 
$
\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
$

\noindent \textbf
{Step 7. Result download}\label{step-7-results-download} 
Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{result}$.

Symbolically: 
$
\mathrm{result} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
$

@@

We analyze the fairness of the protocol by representing it as an interactive non-cooperative game.

@@

\begin{itemize}
\item
  Neutral position (•): when a party hasn't spent nor gained anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item
  Disadvantaged position (-): when a party has put a significant value without receiving an equivalent. For example, paid for a service in advance.
\item
  Advantaged position (+): when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
\end{itemize}

There are many actions that each party can take, but we group them into two categories:

@@

\item
  Normal: taking the action prescribed by the protocol.
\item
  Abnormal: everything that deviates from the designed steps of the protocol. For example, sending an arbitrary message, skipping some step, repeating step, timing out.
\end{enumerate}

Moreover, at any step of the protocol, the customer can start a dispute; therefore, another dimension with two positions has to be considered:

@@

\item
  Agree: the customer agrees with the action and therefore does not start a dispute.
\item
  Start a dispute: the customer does not agree with the action and therefore starts a dispute.
\end{enumerate}

@@

The protocol terminates after the last step, after starting a dispute, or after a party hasn't completed its designated action in time. Therefore, all positions except $\sigma_\mathrm{n}$ are termination positions.

Because the customer is anonymous the SP can not start a dispute---there is no means to identify the customer. To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehavior of the SP makes him win the case.

@@

Below  we listed
assumptions we took
for the analysis purpose.

@@

\item
  Both parties start from a neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialize and complete the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no intermediate steps.
\item
  Repeating the first step starts a new transaction. Repeating any other step is considered abnormal and gets ignored. For example, paying for the invoice twice does not cause any effect on the curse of the protocol.
\item
  Once published, the result is available to the customer in the content storage. The idea of guaranteeing it cryptographically is discussed in Section~\ref{sec:future-work}.

\item
  The protocol can go only forward, there is no way of reverting any action.
\item
  Losing the dispute leads to a punishment that is greater than any reward, which leads to a disadvantaged position (-). Hence, the rational customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to a neutral position (•).
\item
  Both the customer and the SP are rational (selfish). They always prefer to go from worst position to better position, but also risk temporary worst position in favor of a later better position iff it's assured that they won't be stuck in the worst position.
\end{itemize}

@@

Figure~\ref{fig:positions} 
shows the positions of each party after each possible action taken.

\begin{figure}[h!]
\includegraphics[width=9cm]{formal-table-of-positions.png}
\centering
\caption{Positions after each step of protocol}
\label{fig:positions}
\end{figure}

Below we describe each step and rationale of the outcome position.

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position. One would argue that the customer has put effort of
    delivering the materials to the SP, or that the sample is valuable.
    We assume that the sample without personal information is useless
    and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he didn't put any effort to hence the package, also the package hasn't any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\sigma_{1, c, \mathrm{d}} = -\), the customer loses the case as the SP has still an opportunity to publish proof-of-provision within the timeframe.
  \item
    \(\sigma_{1, s, \mathrm{d}} = \sbullet\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol and move to a non-disadvantaged
  position \(\sigma_{1, c, \mathrm{n}} = \sbullet\).
\item
  The SP can do nothing and end up in a non-disadvantaged position
  \(\sigma_{1, s, \mathrm{n}} = \sbullet \) or
  \(\sigma_{1, s, \mathrm{d}} = \sbullet \).
\end{itemize}

@@

SP has published the \textbf{incorrect} result on time:
